Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.

### 2014-11-08 Paper/supplementary.tex
Cleaned up the model.pdf to make it look more like a paper.

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim} % for comment environment
% \usepackage{soul} % for \hl highlighting
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}
\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
\author{Vikas Dhiman\\
{\tt\small vdhiman@nec-labs.com}
\and
Manmohan Chandraker\\
{\tt\small manu@nec-labs.com}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  The long term goal of this project is to identify and represent commonly 
  occurring potentially dangerous road situations where driver can be warned 
  about the situations. Such kind of driver assistance requires understanding
  the state of various road scene elements. We broadly categorize the elements
  in the scene as traffic participants (TP) and as other "scene elements" (like
  lanes, intersections etc). 
\end{abstract}

\section{Introduction}
  NEC has already developed a monocular camera based structure from motion
  system which is accurate for requirements of road scene understanding. So we
  assume that egomotion is given as an observed variable in our graphical
  model. And we have following features to our disposal for estimating the 3D
  poses (position + orientation) of traffic participants:
  \begin{description}
    \item[Ground plane] We assume that all the traffic participants lie on a common ground
      plane. This is not particularly true for the cars that are parked off the
      road. However, for autonomous driver assistance applications we can
      ignore those cars.
    \item[Detections] We assume that 2D car detections are available with tracking informations.
    \item[Point tracks] We assume that 2D point tracks are available.
    \item[GPS and Map information] We assume that GPS information is available
      and we use openstreetmaps.org for pulling out local map for the current
      car's position.
    \item[Lane Information] We assume the lane detection works well and lane
      information is available.
    \item[Size prior] The distribution of size of cars follows gaussian distribution.
    \item[Collision] A reasonable output of the system donot has any overlapping cars.
  \end{description}

\section{Notation}
% 3D pose of the cars and ego motion
\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}

@@

\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}

\begin{table}[h]
  \begin{tabular}{|l|l|}
    \hline
    Symbol & Meaning \\
    \hline
    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
    $\egop$ & Position of camera at time $t$\\
    $\egoo$ & Orientation of camera at time $t$\\
    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
    $\bb{i}$ & 2D bounding box of the car in image\\
    \hline
  \end{tabular}
\end{table}

%%%%%%%%% BODY TEXT
\section{The Model}

The objective is to find the most likely traffic participant state given various
evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.}, \text{map},
\text{GPS}\}$.

Mathematically, find:
\begin{align}
  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
\end{align}

Bayes rule
\begin{align}
  P(\{\state{i}{t}\} | \mathbb{E}) &=
  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
\end{align}

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
  \caption{Graphical model. The six numbered black circles represent the
    unknown state variables of each car. All other nodes in the graphical model
    are assumed
    observed variables. Consider each energy in the model one by one. (1)
    Bounding box energy: The bounding box energy without occlusion modeling is
    a unary term, but with occlusion it becomes a higher order term that
    affects the state of occluder as well. In this graphical model we assume
    that the scene is being observed from left to right, hence "2" occludes "6"
    and "5" and "5" occludes "1". The bounding box detection is represented by
  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
  included in modeling point tracks energy we have similar interdependencies
  for point tracks energy. The available point tracks are modeled by
  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
  mathematically is a dense graph between all the TP but here we represent
  collision among only those TP that are near enough to have a significant
collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
  \label{fig:graphmodel}
\end{figure}

Assume conditional independence according to graphical model in
\ref{fig:graphmodel}.

\begin{multline}
  P(\{\state{i}{t}\} | \mathbb{E}) =
  \frac{1}{Z}
  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
%
  \prod_{i=1}^{N}
  \prod_{t=s_i}^{e_i}
  P(\bb{i} | \state{i}{t})
  P(\trackp{t} | \state{i}{t})\\
  P(\state{i}{t} | L_m(t))
  P(\state{i}{t} | \state{i}{t-1})
  P(\state{i}{t})
\end{multline}

We can formulate similar objective function in negative log domain:
\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
    \WEnergy{box}
  + \WEnergy{track}\\
  + \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{prior}
\end{multline}

\subsection{Collision energy}

Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity of two
distributions $p(x)$ and $q(x)$. If we represent traffic participants as
gaussians in BEV, then similarity is a measure of collision. Exactly
overlapping distribution results in coefficient as 1. The analytical form of
Bhattacharya coefficient has been taken from
\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}

\begin{align}
  \label{eq:collisionEnergyHellingerDistance}
  \EnergyCol &=
  \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
  {|P|^\frac{1}{2}}
  e^{-\frac{1}{8}
    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
    P^{-1}
    \left(\pos{i}{t} - \pos{j}{t}\right)
    }
\end{align}
where 
\begin{align}
  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l^i & 0 \\ 0 & 2/w^i \end{bmatrix}
R_{\ori{i}{t}}
\end{align}

@@

  \newcommand{\minx}{x_{\text{min}}}
  \newcommand{\miny}{y_{\text{min}}}
  \newcommand{\maxx}{x_{\text{max}}}
  \newcommand{\maxy}{y_{\text{max}}}
  \newcommand{\frontface}{F^i_\text{FF}(t)}
  Each bounding box has 6 faces of which only 3 can be visible.
  Sort the vertices in increasing order of depth. The closest vertex has three
  neighboring faces. All the faces that are visible must be a subset of these
  three. Use first three vertices to
  define the front face (say $\frontface$). Also identify the four 3D points
  that correspond to min/max in x and y direction in the image. If all min-max 4
  points are same as vertices of $\frontface$, then we have only one plane
  visible. If $\{\minx, \maxx\} \not\subset \frontface \land \{\miny, \maxy\}
  \not\subset \frontface$ then we have 3 planes visible. Otherwise we have just
  two planes visible. Let number of planes visible be $n_F$.

@@

\newcommand{\occ}[1]{o({#1})}
\newcommand{\face}{F^i_k(t)}
\begin{comment}
  \subsubsection{Occlusion mask}
  % Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
  % \begin{itemize}
  %   \item Sort all cars in increasing order of depth
  %   \item for each car $i$ in the sorted list
  %     \begin{itemize}
  %       \item Update mask polygon: \\
  %         $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\dimsn{i}}$
  %       \item $d = \relpz{i}{t}$
  %     \end{itemize}
  % \end{itemize}

@@

  where $\relpz{j}{t}$ is the depth of the $j$th traffic participant when sorted
  by increasing depth.

@@

\subsection{Continous Point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We want continuous modeling of occlusion. We model occlusion as a opacity
term. Based on the dimensions $\dimsn{i}$, we can
compute the covariance matrix $\Sigma_i$ as shown in Sec. 
\ref{sec:sigmacomputation}

So far we have modeled our point tracks energy in a non-smooth way:
\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t-1}}(#1)}
\begin{multline}
  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty a_j^i(\lambda)\|\trackpj{t} - \projectionOf{\invProjectionOf{\trackpj{t-1}}}\|^2 d\lambda
\end{multline}

The tricky part here is inverse projection $\invProjectionOf{.}$ . When we
project an image point back to 3D we get a ray $\lambda K^{-1}\trackpj{t-1}$
which is ambiguous up to a scale factor $\lambda$. Using our hypothesized 3D
layout of the scene we can estimate this scale factor, we
can compute a distribution over the $\lambda$. 
\subsubsection{Occupancy function}
Assuming occupancy to be a
probability distribution over 3D space. For each traffic participant the
occupancy is modeled as a logistic function 
\newcommand{\occf}{f^i_{occ}(\mathbf{x})}
\begin{align}
   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
\end{align}
where $L(.)$ is the logistic function defined by
\begin{align}
  L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
    }
\end{align}
where $d(\mathbf{x},\pos{i}{t-1}) =
(\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
0.9$

We model the probability of a point being projected to a camera is dependent
up two factors, (1) reflection and (2) transmission through intermediate
space. 
\subsubsection{Reflection probability}
For lambertian reflection we replace the surface normal with the
gradient of occupancy.
\begin{align}
  P_{\text{reflection}} = \sum_i (\max \{0, \nabla \occf^\top
  \hat{\mathbf{r}_j}\})^2
\end{align}
where $\hat{\mathbf{r}_j} =
\frac{K^{-1}\trackpj{t-1}}{\|K^{-1}\trackpj{t-1}\|}$ is unit vector in the
direction of ray. The gradient in the direction opposite to ray yields -ve
probability which needs to be clipped off. Squaring the function keep it
smooth near zero.

\subsubsection{Transmission probability}
A model for transmission of light through a material of thickness $x$,
density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
\begin{align}
  I(x) = I_0e^{-k_o\rho x}
\end{align}

Since both opacity and density are represented by our occupancy function
$\occf$, and also the domain of our $\occf$ is $[0, 1]$ instead of $[0,
\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by our transparency
function $1 - \occf$. So the transmission probability over a small distance
$d\lambda$ is given by
\begin{align}
  P_{\text{transmission}}(\lambda + d\lambda) =
  P_{\text{transmission}}(\lambda) (1-\occf)^{d\lambda}
\end{align}
\newcommand{\ray}{\hat{\mathbf{r}}_j}
\newcommand{\occfray}{f_{occ}(\lambda\ray)}

For our given ray $\mathbf{x}_j = \lambda \ray$, the probability that the point
$\trackpj{t-1}$ is reflected from a distance $\lambda$ is given by

\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}
\begin{align}
  \lambdadist &= P_{\text{reflection}}
  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} %\\
  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
\end{align}
where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
$\lambda$. A product integral is a simple integral in log domain
\begin{align}
  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
  e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
\end{align}

% Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
% reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
% $\lambda$. Let

\subsubsection{Reprojection error}

\begin{align}
  f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
  \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
  %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
  &= \frac
  {p_{1:2}\lambda + q_{1:2}}
  {p_{3}\lambda + q_{3}}
\end{align}
where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
$q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$

Now that we have an association from TP $i$ to point track $j$ through
$\lambda$, we can come up with an association probability
\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\assocP}{a^{i}_{j,t-1}(\lambda)}
\newcommand{\assocPk}{a^{i}_{j,t-1}(\lambda_k)}
\begin{align}
   \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
\ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
&=(\max \{ 0, \nabla \occf^\top \ray \})^2
  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
\end{align}

Note that this fraction although called association probability does not
capture the entire information that we have available for compute association
of points to tracks. This above fraction is the association probability given 
the hypothesized parameters of traffic participant model. Given that a point is
observed on the image the sum of probability marginalized over other parameters
must be one i.e.
\begin{align}
    \sum_{i = 1}^N
    \int_1^{\infty}
    \assocP d\lambda = 1
\end{align}

To compute the association probability between traffic participant $i$ and
point track $j$ we must use re-projection error as well. When the association
$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
re-projection error must be zero, otherwise the error becomes a measure of
distance from the true solution:

\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
\begin{align}
  \Ereproj(\lambda) = \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
\end{align}

The error terms can be converted to probability domain by considering the error
term as negative log of probablity

\begin{align}
  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))
\end{align}

Using both the evidence terms we can write probability of association as
\begin{align}
  P^{(ij)}_{\text{assoc}} \propto \int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
  \label{eq:prob-assoc}
\end{align}

However, for estimating the overall energy we just need to compute the expected
value of the re-projection error for given parameters, i.e.

\begin{multline}
  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i,\{ \dimsn{i} \}_i) = \\
    \sum_{i = 1}^N
    \sum_{j = 1}^{M}
    \int_1^{\infty}
    a^i_{j,t-1}(\lambda) 
    \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
    d\lambda
\end{multline}

If the aim is to find the best possible association, it is easier as we need to
to compute the association that minimizes the expected re-projection error for
point $j$. It remains to be seen that how the minima of following expression relates to minima of \eqref{eq:prob-assoc}

\begin{align}
  i^* = \argmin_{i=1}^N \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
\end{align}

Since the computation of $\assocP$ entirely depends on hypothesized parameters,
it severely limits the applicability of this method outside this kind of
parameterized model.

\subsubsection{Approximations}
\newcommand{\Ptrans}{P_{\text{transmission}}}
\newcommand{\Prefl}{P^i_{\text{reflection}}}
\newcommand{\dishort}{d_i(\mathbf{x})}

Reflection probability of $i$th traffic participant is easy to compute
analytically 
\begin{multline}
  \Prefl =
  (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
  = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
  \label{eq:analytic-prefl}
\end{multline}
where 
\begin{multline}
  \nabla \occfxi^\top\ray \\=
  \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
\end{multline}
where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
\usepackage{verbatim} % for comment environment
% \usepackage{soul} % for \hl highlighting
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% 3D pose of the cars and ego motion
\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}

@@

\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
\newcommand{\minx}{x_{\text{min}}}
\newcommand{\miny}{y_{\text{min}}}
\newcommand{\maxx}{x_{\text{max}}}
\newcommand{\maxy}{y_{\text{max}}}
\newcommand{\frontface}{F^i_\text{FF}(t)}

\newcommand{\occ}[1]{o({#1})}
\newcommand{\face}{F^i_k(t)}

\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
\newcommand{\occft}[1]{f_{occ}(#1)}

\newcommand{\ray}{\hat{\mathbf{r}}_j}
\newcommand{\occfray}{f_{occ}(\lambda\ray)}
\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}

\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\assocP}{a^{(ij)}(\lambda)}
\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}

\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
\newcommand{\dishort}{d_i(\mathbf{x})}

\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}

\newcommand{\Gauss}{\mathcal{N}}
\newcommand{\PropDist}{\mathcal{W}_j}

\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}

\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}

\newcommand{\muit}{\mu^(i)_t}
\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}

\newcommand{\muic}{{\mu^(i)_c}}
\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}

\newcommand{\muiu}{\mu^{(i)}_t}
\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}

\newcommand{\xt}{\mathbf{x}_t}
\newcommand{\xc}{\mathbf{x}_c}

\newcommand{\Rctot}{R}
\newcommand{\tctot}{t}

\newcommand{\tcmut}{t'}

\newcommand{\Beizer}{B\'eizer }

\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}

\begin{document}
\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
\author{Vikas Dhiman\\
  University of Michigan\\
  Ann Arbor, MI, USA\\
{\tt\small dhiman@umich.edu}
\and
Manmohan Chandraker\\
NEC Laboratories America, Inc.\\
Cupertino, CA, USA\\
{\tt\small manu@nec-labs.com}
\and
Jason J Corso\\
  University of Michigan\\
  Ann Arbor, MI, USA\\
{\tt\small jjcorso@eecs.umich.edu}
}
\maketitle

\section{Supplementary Material}

\subsection{Numerical integration}
Numerical integration is possible by computed by sampling. Samples need to be
generated from the association probability $\assocP$ for a given $j$. We take
proposal distribution to be a GMM with modes around probable reflection points.
The weights of all Gaussians in the mixture are proportional to the distance of
the point $j$ from projection of ellipsoid centre i.e. 
\begin{align}
  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
\end{align}
where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
The range of Gaussian $G_i$
must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
\begin{align}
  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
\end{align}
And the numerical integral with $K$ samples is computed by
\begin{align}
    \int_1^{\infty}
    \assocP
    \Ereproj(\lambda)
    d\lambda
    =
    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
\end{align}
where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.

\subsection{Sigma of ellipsoid}
\label{sec:sigmacomputation}

\begin{align}
  \muit &= \begin{bmatrix}
  0& 0& \frac{h}{2}
  \end{bmatrix}^\top\\
  \Sigmait &= \begin{bmatrix}
    \frac{4}{l^2} & 0 & 0 \\
    0 & \frac{4}{w^2} & 0 \\
    0 & 0 & \frac{4}{h^2}
  \end{bmatrix}
\end{align}

In tracklet coordinates the equation of ellipsoid is 
\begin{align}
  (\xt - \muit)^\top \Sigmait (\xt - \muit) = 1
\end{align}

Moving to camera coordinates
\begin{align}
  (\Rctot \xc + \tctot - \muit)^\top \Sigmait (\Rctot \xc + \tctot - \muit) = 1
\end{align}

Let $\tcmut = \tctot - \muit$
\begin{align}
  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
\end{align}
\begin{align}
  \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
  + \tcmut^\top \Sigmait \tcmut = 1
\end{align}
Let $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
\tcmut$
\begin{align}
  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic +
  \tcmut^\top \Sigmait \tcmut = 1
\end{align}
Let $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
\muic^\top\Sigmaic\muic}$
\begin{align}
(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1
\end{align}

\subsection{Projection of ellipsoid to image}
\newcommand{\mubar}{\bar{\mu}_i}
The perspective projection of an ellipsoid in general is not an ellipsoid in
general. We approximate the projection of ellipsoid by projecting a slice
through the ellipsoid. We choose the slice as the plane perpendicular to the
line joining the center of ellipsoid to the optical center of camera. Let
$\muic$ and $\Sigmaicf$ be the parameters of ellipsoid describing the ellipsoid
in camera coordinates. The any point $x$ on the plane satisfies
$x^\top\frac{\muic}{\|\muic\|} = \|\muic\|$. We introduce 
$\mubar = \frac{\muic}{\|\muic\|^2}$ for notational simplicity. Hence, we want
to project the points that satisfy both the equation of chosen plane and the 
ellipsoid i.e.
\begin{align}
  \mubar^\top x = x^\top\mubar &= 1\\ 
  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \enspace.
\end{align}
We rewrite $\muic = \muic\mubar^\top x$, and $1 = x^\top\mubar \mubar^\top x$
\begin{align}
  (x-\muic\mubar^\top x)^\top\Sigmaicf(x-\muic\mubar^\top x) &= x^\top\mubar \mubar^\top x \enspace,
\end{align}
which is equivalent to 
\begin{align}
  x^\top\left((I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top\right)x &= 0\enspace.
\end{align}

Note that if $u$ is a projection of $x$ to camera with intrinsic parameters
$K$, then $x = K^{-1}u$ where $u$ is in homgeneous coordinates. Hence the above equation can be re-written as
\newcommand{\Sproj}{\Sigma^{-1}_{\text{proj }i}}
\newcommand{\Sperpcut}{\Sigma^{-1}_{\text{perpcut }i}}
\begin{align}
  u^\top\Sproj u &= 0\enspace, 
\end{align}
where $\Sproj = K^{-\top}\Sperpcut K^{-1}$ and 
\begin{align}
  \Sperpcut = (I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top \enspace.
\end{align}

@@

  Each bounding box has 6 faces of which only 3 can be visible.
  Sort the vertices in increasing order of depth. The closest vertex has three
  neighboring faces. All the faces that are visible must be a subset of these
  three. Use first three vertices to
  define the front face (say $\frontface$). Also identify the four 3D points
  that correspond to min/max in x and y direction in the image. If all min-max 4
  points are same as vertices of $\frontface$, then we have only one plane
  visible. If $\{\minx, \maxx\} \not\subset \frontface \land \{\miny, \maxy\}
  \not\subset \frontface$ then we have 3 planes visible. Otherwise we have just
  two planes visible. Let number of planes visible be $n_F$.

@@

\begin{comment}
  \subsubsection{Occlusion mask}
  % Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
  % \begin{itemize}
  %   \item Sort all cars in increasing order of depth
  %   \item for each car $i$ in the sorted list
  %     \begin{itemize}
  %       \item Update mask polygon: \\
  %         $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\dimsn{i}}$
  %       \item $d = \relpz{i}{t}$
  %     \end{itemize}
  % \end{itemize}

@@

  where $\relpz{j}{t}$ is the depth of the $j$th TPs participant when sorted
  by increasing depth.

@@

\begin{comment}%%%%%%%%%%%%% May or may not use %%%%%%%%%%%
TODO: Write Introduction
  NEC has already developed a monocular camera based structure from motion
  system which is accurate for requirements of road scene understanding. So we
  assume that egomotion is given as an observed variable in our graphical
  model. And we have following features to our disposal for estimating the 3D
  poses (position + orientation) of traffic participants (TPs):
  \begin{description}
    \item[Ground plane] We assume that all the TPs lie on a common ground
      plane. This is not particularly true for the cars that are parked off the
      road. However, for autonomous driver assistance applications we can
      ignore those cars.
    \item[Detections] We assume that 2D car detections are available with tracking informations.
    \item[Point tracks] We assume that 2D point tracks are available.
    \item[GPS and Map information] We assume that GPS information is available
      and we use openstreetmaps.org for pulling out local map for the current
      car's position.
    \item[Lane Information] We assume the lane detection works well and lane
      information is available.
    \item[Size prior] The distribution of size of cars follows gaussian distribution.
    \item[Collision] A reasonable output of the system donot has any overlapping cars.
  \end{description}
\end{comment}

\begin{comment}
  Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
  affect of uncertainty on mean and variance of existing observations. On adding
  noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
  \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
  \begin{multline}
    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) \\
    + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
  \end{multline}
  where the terms $E(x \Delta x^\top)$ denote the correlation between the data
  vector and the uncertainty in the data. Although we understand that in our case
  the data is the appearance based detection score and uncertainty because of
  occlusion is closely related to the appearance and hence detection score, we
  assume independence between $x$ and $\Delta x$. Hence our resultant covariance
  matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
  are 4D. But that should not be a problem because the detection scores are
  modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
  y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
  domain as the regions are independent of min or max variation. The parameters
  of 4D occlusion distribution are given by
